Open archaeology, open source?

### 2023-09-20 analysis/_06-network.qmd
Rearrange sections a bit
Add tbl-repo-centrality

## Network analysis

@@

**NOTE:** Create a table containing the nodes with highest betweenness centrality from the repo-repo graph. Columns should specify the name of the repository, the number of commits, the category, and tags. If possible also include a summary of the pulse as a line chart with x axis as time and y axis as activity. This will allow us to identify the characteristics of these repositories that prompt greater integration.

>>>>

# An emerging community of practice? <!-- Results III: network analysis of collaborative communities -->

@@

```{r tbl-repo-centrality}
#| tbl-cap: The sixteen most central repositories according to the repository–repository network analysis
oarch_graph_repo_repo |>
  mutate(centrality = centrality_betweenness()) |>
  as_tibble() |>
  arrange(-centrality) |>
  slice(1:16) |>
  left_join(oarch, c("repo" = "gh_repo")) |>
  mutate(n_commits = map_int(gh_commits, nrow)) |>
  unite(tags, tag1:tag5, sep = "; ", na.rm = TRUE) |>
  select(repo, centrality, category, tags, n_commits) |>
  gt() |>
  cols_label(
    repo = "Repository", 
    centrality = "Betweenness Centrality",
    category = "Category",
    tags = "Tags",
    n_commits = "Commits"
  )
```
